Verifying Spatial Properties of Stencil Computations

### 2016-11-16 paper.tex
Gloves are off. Remove courtesy notation explanation. Typo fix.
Clean up generalisation

\begin{definition}
  An \emph{index scheme} is a vector of size $n$ (an $n$-vector) with
  values drawn from $\domainVal = \mathbb{Z} \cup \{\infty\}$.  Values
  in $\mathbb{Z}$ represent the offsets of neighbourhood indices
  (\ie{}, the constant integer $c$ in an indexing expression of the
  form $i \pm c$, Def.~\ref{def:neighbour}) and $\infty$ is a wild-card
  representing both constant indices and unspecified indices. Throughout, $u, v,
  w$ range over
  index schemes and $u_i$ denotes the $i^{th}$ element of $u$. We
  write $(\domainVal)^n$ for the set of all $n$-dimensional schemes.
\end{definition}

Indexing schemes give an abstracts array subscripts.
Our model represents the meaning of stencil specifications
as indexing schemes, which explain the range of possible
indexing behaviours which are consistent with the specification.
The relationship between source language
terms and indexing terms
 is given precisely by the following function \textsf{schematic},
 which forms part of checking and inference (\S\ref{sec:analysis}).

@@

\begin{definition}[Generalisation]
Given two schemes $v, w$ of dimensionality $n$,
then $w$ is said to \emph{generalise} $v$
(or conversely $v$ \emph{specialises} $w$),
written $v \preceq_n w$, iff the following holds:
%%
\[
v \preceq_n w \;\; \Leftrightarrow  \;\;
  \forall i\!\in\!\{ 1, \ldots, n \} . \, (w_i = \infty \, \vee \, v_i = w_i)
\]
%%
That is, two schemes are related by the (reflexive and transitive) binary relation
$\preceq_n$ over $(\mathbb{Z}_{\infty})^n$ if in each dimension
the two schemes are equal or $w_i = \infty$
in place of some $\mathbb{Z}$ in $v_i$ for $v \preceq_n w$.
Thus, the element $\infty$ generalises any index in the same dimension.
%
\end{definition}

>>>>

\begin{definition}
  An \emph{index scheme} is a vector of size $n$ (an $n$-vector) with
  values drawn from $\domainVal = \mathbb{Z} \cup \{\infty\}$.  Values
  in $\mathbb{Z}$ represent the offsets of neighbourhood indices
  (\ie{}, the constant integer $c$ in an indexing expression of the
  form $i \pm c$, Def.~\ref{def:neighbour}) and $\infty$ is a wild-card
  representing both constant indices and unspecified indices.
  For an index scheme $u$, $u_i$ denotes the $i^{th}$ element of $u$. We
  write $(\domainVal)^n$ for the set of all $n$-dimensional schemes.
\end{definition}

Indexing schemes abstract array subscripts.
Our model represents the meaning of stencil specifications
as indexing schemes, which explain the range of possible
indexing behaviours which are consistent with the specification.
The relationship between source language
terms and indexing terms
 is given precisely by the following function \textsf{schematic},
 which forms part of checking and inference (\S\ref{sec:analysis}).

@@

\begin{definition}[Generalisation]
Given two schemes $v, w$ of dimensionality $n$,
then $w$ is said to \emph{generalise} $v$
(or conversely $v$ \emph{specialises} $w$),
written $v \preceq_n w$, iff the following holds:
%%
\[
v \preceq_n w \;\; \Leftrightarrow  \;\;
  \forall i\!\in\!\{ 1, \ldots, n \} . \, (w_i = \infty \, \vee \, v_i = w_i)
\]
%%
Two schemes are related by the (reflexive and transitive) binary relation
$\preceq_n$ over $(\mathbb{Z}_{\infty})^n \times (\mathbb{Z}_{\infty})^n$.
The element $\infty$ generalises any index in the same dimension.
%
\end{definition}
